Mapping malaria in pre-elimination settings by sharing spatial information between incidence and prevalence datasets

### 2019-08-06 ms.tex
Add author summary and keywords.

>>>>

\section{Summary}

We present a comparison of two methods for combining malaria prevalence surveys and aggregated incidence count data using case studies in Indonesia, Senegal and Madagascar. 
The first method fits a spatial Gaussian random field to the prevalence data which is then used as a covariate in a disaggregation regression model.
The second is a full joint model that simultaneously fits a disaggregation regression model to the incidence data and prevalence surveys.
We compare both models to a baseline disaggregation regression model and find that the simpler model works the best.

\subsection{Keywords}
Disaggregation regression, disease mapping, geostatistics, joint modelling, spatial statistics.
